Invasive lionfish present region-wide variation of allometric growth in the Western Atlantic

### 2018-04-09 docs/Manuscript.Rmd
Modified intro

# Introduction

@@

A significant amount of research has been done to describe lionfish feeding ecology in North Carolina \citep{muoz_2011}, the Bahamas \citep{morris_2009,cote_2013}, Northern Gulf of Mexico \citep{dahl_2014}, Mexican Caribbean \citep{valdezmoreno_2012,villaseorderbez_2014}, Belize \citep{hackerott_2017}, and Costa Rica \citep{sandel_2015}. Their feeding behavior and high consumption rates can reduce recruitment \citep{albins_2008} and population sizes \citep{green_2012} of native reef-fish species, and further the endangerment of critically endangered reef fish \citep{rocha_2015}. (However, see \citet{hackerott_2017} for a case where there was no evidence that lionfish affected the density, richness, or community composition of prey fishes). Major efforts have been made to understand the possible impacts of the invasion by keeping track of its range through time \citep{schofield_2009,schofield_2010} and predicting invasion ranges under future climates \citep{grieve_2016}. By combining information from these disciplines, researchers have been able to predict the trophic impacts of lionfish \citep{ariasgonzalez_2011}, which can then be translated into ecosystem-level and economic impacts.

@@

The feasibility of lionfish removal programs has been extensively evaluated through field observations\citep{usseglio_2017,sandel_2015,chin_2016,deleon_2013} and empirical modeling \citep{barbour_2011,morris_2011,johnston_2015}. The latter approeach models changes in biomass in response to changes in mortality (*i.e.* culling). In this case, biomass represents the sum of all fish's individual weight. The individual weight of an organism (Total Weight; TW) can be estimated from its Total Length (TL) using the allometric growth equation ($TW = aTL^b$). Parameters $a$ and $b$ for this equation exist for North Carolina \citep{barbour_2011}, Northern \citep{fogg_2013,dahl_2014} and Southern Gulf of Mexico \citep{aguilarperera_2016}, the Southern Mexican Caribbean \citep{sabidoitza_2016}, Bahamas \citep{darling_2011}, Little Cayman \citep{edwards_2014}, Jamaica \citep{chin_2016}, Bonaire \citep{deleon_2013} Puerto Rico \citep{toledohernndez_2014}, and Costa Rica \citep{sandel_2015}, but remain unavailable for the central Mexican Caribbean. The weight-at-length of a species can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}. Thus, when using biomass-informed models or estimating weights from length observations, it is important to use site-specific parameters. This is especially important when research involves identifying the total biomass available for harvest by fishers \citep{chin_2016} or the efficacy of lionfish removals \citep{barbour_2011,morris_2011,johnston_2015}.

@@

# Materials and Methods

>>>>

\section*{Introduction}

@@

A substantial amount of research has been done to describe lionfish feeding ecology in North Carolina \citep{muoz_2011}, the Bahamas \citep{morris_2009,cote_2013}, Northern Gulf of Mexico \citep{dahl_2014}, Mexican Caribbean \citep{valdezmoreno_2012,villaseorderbez_2014}, Belize \citep{hackerott_2017}, and Costa Rica \citep{sandel_2015}. Their feeding behavior and high consumption rates can reduce recruitment \citep{albins_2008} and population sizes \citep{green_2012} of native reef-fish species, and further the endangerment of critically endangered reef fish \citep{rocha_2015}. (However, see \citet{hackerott_2017} for a case where there was no evidence that lionfish affected the density, richness, or community composition of prey fishes). Major efforts have been made to understand the possible impacts of the invasion by keeping track of its range through time \citep{schofield_2009,schofield_2010} and predicting invasion ranges under future climates \citep{grieve_2016}. By combining information from these disciplines, researchers have been able to predict the trophic impacts of lionfish \citep{ariasgonzalez_2011}, which can then be translated into ecosystem-level and economic impacts.

@@

The feasibility of lionfish removal programs has been extensively evaluated through field observations\citep{usseglio_2017,sandel_2015,chin_2016,deleon_2013} and empirical modeling \citep{barbour_2011,morris_2011,johnston_2015}. The latter approeach models changes in biomass in response to changes in mortality (*i.e.* culling). In this case, biomass represents the sum of all fish's individual weight. The individual weight of an organism (Total Weight; TW) can be estimated from its Total Length (TL) using the allometric growth equation ($TW = aTL^b$). Parameters $a$ and $b$ for this equation exist for North Carolina \citep{barbour_2011}, Northern \citep{fogg_2013,dahl_2014} and Southern Gulf of Mexico \citep{aguilarperera_2016}, the Southern Mexican Caribbean \citep{sabidoitza_2016}, Bahamas \citep{darling_2011}, Little Cayman \citep{edwards_2014}, Jamaica \citep{chin_2016}, Bonaire \citep{deleon_2013} Puerto Rico \citep{toledohernndez_2014}, and Costa Rica \citep{sandel_2015}, but remain unavailable for the central Mexican Caribbean. The length-weight of a species can vary across regions as a response to biotic (*e.g.* local food availability) and abiotic (*e.g.* water temperature) conditions \citep{johnson_2016}. Thus, when using biomass-informed models or estimating weights from length observations, it is important to use site-specific parameters. This is especially important when research involves identifying the total biomass available for harvest by fishers \citep{chin_2016} or the efficacy of lionfish removals \citep{barbour_2011,morris_2011,johnston_2015}.

@@

\section*{Materials and Methods}
